Additional analysis

### 2018-07-15 03_additional-analysis.Rmd
Add session info
Shrink time figure

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_ms) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos() +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "avg-time.png"),
         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
```

@@

>>>>

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_ms) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos(base_size = 9.5) +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = here("output", "figures", "avg-time.pdf"),
         width = 4, height = 2.25, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "avg-time.png"),
         width = 4, height = 2.25, units = "in", type = "cairo", dpi = 300)
```

@@

# Session info

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info}
sessionInfo()
```

</div>
